---
title: "Assignment1-FML"
author: "Masuma"
date: "2024-02-04"
output:
  html_document: default
  pdf_document: default
---

```{r}
##Executive Summary
#Here I have imported a file from web which consists of both  quantitative and qualitative variables on apple quality.I have tried to show the descriptive analysis and relevant plotting on that same Dataset.
```

***

##Assigning value of may_dataset by importing csv file from external source

##source-https://www.kaggle.com/datasets/nelgiriyewithana/apple-quality
```{r}
my_dataset <- read.csv("C:/Users/user/Desktop/FML Assignment/apple_quality.csv") 
```

##Descriptive statistics for  quantitative and categorical variables
```{r}
summary(my_dataset)
```

##Dimension of my dataset
```{r}
dim(my_dataset)
```

##Class and structure of my dataset
```{r}
class(my_dataset)
str(my_dataset)
```

##Showing mean of a specific column-crunchiness
```{r}
mean(my_dataset$Crunchiness)
```

##variable transformation
```{r}
as.character(my_dataset$Weight)
```

##Plotting one quantitative variable
```{r}
plot(my_dataset$Sweetness, my_dataset$Acidity)
```

##Plotting the data by using Histogram
```{r}
hist(my_dataset$Sweetness)
```

##Conclusion
The whole data set on Apple quality shows various features of apples and here I have done analysis on descriptive and graphical perspective statistics.

